\LARGE \bf Exploiting Non-Slip Wall Contacts \\ to Position Two Particles Using The Same Control Input

### 2018-05-30 journalWallFriction/simulation.tex
Added numbers.
changed hits to contacts

\end{overpic}
\begin{overpic}[width =\figwid]{identical.png}\put(-2,6){\begin{turn}{90} \tiny{interchangeable particles}
\end{turn}}
\end{overpic}
}\caption{\label{fig:contourPlots}{Starting positions of particles $1$ and $2$ and goal position of particle $2$ are fixed, and $\epsilon=0.001$.
 The top row of contour plots show the distance if robot $1$'s goal position is varied in $x$ and $y$. The middle row shows the number of moves required for the same configurations. The bottom row shows the same configuration but when the particles are interchangeable.}
\vspace{-1em}
}
\end{figure}
Algorithm \ref{alg:optimalAlg}  was implemented in Mathematica using particles with zero radius. Figure \ref{fig:reachableSet} shows frames of the algorithm in two representative workspaces, square and disk, with two arbitrary starting and goal configurations.
%An online interactive demonstration and source code of the algorithm are available at \cite{Shahrokhi2015mathematicaParticle}.
%  Fig.~\ref{fig:shapeControlMathematica1}  shows  an implementation of this algorithm with robot initial positions represented by hollow squares and final positions by circles. 
 %Dashed lines show the shortest route if robots could be controlled independently, while solid lines show the optimal shortest  path using uniform inputs.

@@

%The path length grows when the goals have $\pi$ difference and are very close to the boundary. 
 The worst-case occurs when the ending points are at antipodes along the boundary ($\pi$ angular distance). This can never be achieved but can be asymptotically approached as shown in Fig.~\ref{fig:deltanumdist}. 
 Figure \ref{fig:contourPlots} shows the same concepts in a square workspace. Figure \ref{fig:contourPlots} top and middle row considers the particles for three arbitrary starting and goal positions for the particles. 
 Thus far, this paper has considered the particles to be unique. If particles are interchangeable, the path lengths often decrease. The bottom row of  Fig.~\ref{fig:contourPlots} considers interchangeable particles with the same configuration as the middle row with unique particles. The worst-case path lengths decrease by ??\%, ??\%, and ??\% for the three test cases shown. %TODO: shiva, insert numbers.

>>>>

\end{overpic}
\begin{overpic}[width =\figwid]{identical.png}\put(-2,6){\begin{turn}{90} \tiny{interchangeable particles}
\end{turn}}
\end{overpic}
}\caption{\label{fig:contourPlots}{Starting positions of particles $1$ and $2$ and goal position of particle $2$ are fixed, and $\epsilon=0.001$.
 The top row of contour plots show the distance if particle $1$'s goal position is varied in $x$ and $y$. The middle row shows the number of moves required for the same configurations. The bottom row shows the same configuration but when the particles are interchangeable.}
\vspace{-1em}
}
\end{figure}
Algorithm \ref{alg:optimalAlg}  was implemented in Mathematica using particles with zero radius. Figure \ref{fig:reachableSet} shows frames of the algorithm in two representative workspaces, square and disk, with two arbitrary starting and goal configurations.
%An online interactive demonstration and source code of the algorithm are available at \cite{Shahrokhi2015mathematicaParticle}.
%  Fig.~\ref{fig:shapeControlMathematica1}  shows  an implementation of this algorithm with robot initial positions represented by hollow squares and final positions by circles. 
 %Dashed lines show the shortest route if robots could be controlled independently, while solid lines show the optimal shortest  path using uniform inputs.

@@

%The path length grows when the goals have $\pi$ difference and are very close to the boundary. 
 The worst-case occurs when the ending points are at antipodes along the boundary ($\pi$ angular distance). This can never be achieved but can be asymptotically approached as shown in Fig.~\ref{fig:deltanumdist}. 
 Figure \ref{fig:contourPlots} shows the same concepts in a square workspace. Figure \ref{fig:contourPlots} top and middle row considers the particles for three arbitrary starting and goal positions for the particles. 
 Thus far, this paper has considered the particles to be unique. If particles are interchangeable, the path lengths often decrease. The bottom row of  Fig.~\ref{fig:contourPlots} considers interchangeable particles with the same configuration as the middle row with unique particles. The worst-case path lengths decrease by 33\%, 60\%, and 30\% for the three test cases shown. %TODO: shiva, insert numbers.

### 2018-05-30 journalWallFriction/theory.tex
changed hits to contacts

 \subsection{Example: Shortest Path in a Square Workspace}\label{subsec:square}
 Changing the relative positions of particles in any workspace requires making one particle contact the boundary.
 If the goal configuration cannot be reached in one move but can be reached in three moves, the shortest path has a simple solution. The first move, $m_1$, makes one particle hit a wall, $m_2$ adjusts the relative spacing error  to zero, and $m_3$ takes the particles to their final positions. 
$m_2$ cannot be shortened, so optimization depends on choosing the location where the particle hits the wall. 
 Since the shortest distance between two points is a straight line, reflecting the goal position across the boundary wall and plotting a straight line gives the optimal hit location, as shown in Fig. \ref{fig:reflection}. 
  There are four walls, and four candidate solutions, but some candidate solutions may be invalid because a different boundary is hit before the desired first contact position in move $m_1$ (light grey regions) or  invalid because $m_2$ cannot generate the goal relative spacing (dark grey regions).
 %
\begin{figure}
\centering
\begin{overpic}[width=\columnwidth]{Reflection.pdf}\end{overpic}
\vspace{-2em}
\caption{\label{fig:reflection}
The shortest three-move path that reconfigures two particles has the property that the incident angle equals the reflected angle.
} \vspace{-1em}
\end{figure}
%

>>>>

 \subsection{Example: Shortest Path in a Square Workspace}\label{subsec:square}
 Changing the relative positions of particles in any workspace requires making one particle contact the boundary.
 If the goal configuration cannot be reached in one move but can be reached in three moves, the shortest path has a simple solution. The first move, $m_1$, makes one particle contact a wall, $m_2$ adjusts the relative spacing error  to zero, and $m_3$ takes the particles to their final positions. 
$m_2$ cannot be shortened, so optimization depends on choosing the location where the particle contacts the wall. 
 Since the shortest distance between two points is a straight line, reflecting the goal position across the boundary wall and plotting a straight line gives the optimal contact location, as shown in Fig. \ref{fig:reflection}. 
  There are four walls, and four candidate solutions, but some candidate solutions may be invalid because a different boundary is hit before the desired first contact position in move $m_1$ (light grey regions) or  invalid because $m_2$ cannot generate the goal relative spacing (dark grey regions).
 %
\begin{figure}
\centering
\begin{overpic}[width=\columnwidth]{Reflection.pdf}\end{overpic}
\vspace{-2em}
\caption{\label{fig:reflection}
The shortest three-move path that reconfigures two particles has the property that the incident angle equals the reflected angle.
} \vspace{-1em}
\end{figure}
%

### 2018-05-30 journalWallFriction/theory2robAlgs.tex
changed hits to contacts

\begin{figure}
\centering
\begin{overpic}[width=0.32\columnwidth]{twoRobotRegionH.pdf}\end{overpic}
\begin{overpic}[width=0.32\columnwidth]{twoRobotRegionV.pdf}\end{overpic}
\begin{overpic}[width=0.32\columnwidth]{DeltaConfigSquare.pdf}\end{overpic}
\caption{\label{fig:TwoRegions}
Boundary interaction is used to change the relative positions of the particles. Each particle gets the same control input. 
(left) If particle 2 hits the bottom wall before particle 1 reaches a wall, particle 2 can reach anywhere along the green line, and  particle 1 can move to anywhere in the shaded area. 
(middle) Similarly, if particle 2 hits the right wall before particle 1 reaches a wall, particle 2 can reach anywhere along the green line, and then particle 1 can move to anywhere in the shaded area. 
(right) The 2-move reachable sets in the $\Delta$ configuration space is shown.
}
\end{figure}

\begin{figure*}
\centering
\renewcommand{\figwid}{0.66\columnwidth}
\begin{overpic}[width =\figwid]{anypolygon1.pdf}\put(17,-3){\small{Case 1: $s_1$ does not hit boundary}}\put(28,39){$s_2$}\put(63,50){$s_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{anypolygon2.pdf}\put(25,-3){\small{Case 2: $s_1$ hits boundary}}\put(20,40){$s_2$}\put(55,58){$s_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{anypolygon3.pdf}\put(-6,-3){\small{Polygon generated by first contacts along $\overline{ p_i p_{i+1}}$ }}
\end{overpic}
\caption{\label{fig:polygonAlg}{ Steps to generate  the 2-move reachable set when  one particle collides with edge $\overline{ p_i p_{i+1}}$ of a convex polygonal workspace.}
\vspace{-1em}
}
\end{figure*}
 Figure \ref{fig:polygon} shows six workspaces, their $\Delta$ configuration spaces, and the 2-move reachable sets that correspond to representative initial conditions.
 Figure \ref{fig:TwoRegions} highlights the construction of the 2-move reachable sets for a square workspace. There are four 2-move reachable sets, but the horizontal (and vertical) reachable sets are equivalent in the $\Delta$ configuration space so we can plan in this space and choose between the two options to minimize the total distance.
 % The \emph{2-move reachable set} is the locus of points in the $\Delta$ configuration space corresponding to any two-move sequence where the first move brings one particle into contact with the boundary, and the second move translates the second particle without moving the first. 
Algorithm \ref{alg:polygonReachbale} computes the 2-move reachable set for any convex workspace.
The set is constructed by considering each edge of the workspace. We name each vertex as $p_i$ where $1\leq i \leq n$.
  If one particle hits edge $\overline{ p_i p_{i+1}}$ before the other (one particle will always hit before the other unless the particles are parallel to the wall), the corresponding 2-move reachable set is a polygon, constructed in lines 2-13 of Alg.~\ref{alg:polygonReachbale}. The union of these polygons for all $n$ sides is the 2-move reachable set of $\Delta$ configurations.
Figure~\ref{fig:polygonAlg} illustrates the procedure to construct the  2-move reachable set generated by collisions with the $\overline{ p_i p_{i+1}}$ edge.
% 
 \begin{algorithm}[htb]
\caption{ { \sc ReachableSetPolygon}($s_1,s_2,g_1,g_2, P$)}\label{alg:polygonReachbale}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of starting $(s_1,s_2)$ and goal $(g_1,g_2)$ positions of  two particles. 
$P$ is a list of the vertices of a convex polygon. %RSet contains all the reachable polygons.
\State $R_{\textrm{SET}\gets \{\}}$
\For {$p_i$ in $P$}
\State $p_{i}' \gets s_1 + s_2 - p_i$
\State $p_{i+1}' \gets s_1 + s_2 - p_{i+1}$
\State $L \gets \overline{ p_i' p_{i+1}'}$ \Comment{line $(p_{i}', p_{i+1}')$}
\State $l_i, l_{i+1} \gets $ intersections of $L$ and polygon $P$
\If {$p_{i}'$ not inside polygon $P$}
\State $p_{i}' \gets l_i$
\EndIf
\If {$p_{i+1}'$ not inside polygon $P$}
\State $p_{i+1}' \gets l_{i+1}$
\EndIf
%\State $D \gets$ All vertices $\in [ l_i , l_{i+1} ] $
\State $D \gets$ $s_2 - s_1 -([l_i, v_{\textrm{min}}, ..., p_i ] -p_i' $,

>>>>

\begin{figure}
\centering
\begin{overpic}[width=0.32\columnwidth]{twoRobotRegionH.pdf}\end{overpic}
\begin{overpic}[width=0.32\columnwidth]{twoRobotRegionV.pdf}\end{overpic}
\begin{overpic}[width=0.32\columnwidth]{DeltaConfigSquare.pdf}\end{overpic}
\caption{\label{fig:TwoRegions}
Boundary interaction is used to change the relative positions of the particles. Each particle gets the same control input. 
(left) If particle 2 contacts the bottom wall before particle 1 reaches a wall, particle 2 can reach anywhere along the green line, and  particle 1 can move to anywhere in the shaded area. 
(middle) Similarly, if particle 2 contacts the right wall before particle 1 reaches a wall, particle 2 can reach anywhere along the green line, and then particle 1 can move to anywhere in the shaded area. 
(right) The 2-move reachable sets in the $\Delta$ configuration space is shown.
}
\end{figure}

\begin{figure*}
\centering
\renewcommand{\figwid}{0.66\columnwidth}
\begin{overpic}[width =\figwid]{anypolygon1.pdf}\put(12,-3){\small{Case 1: $s_1$ does not contact boundary}}\put(28,39){$s_2$}\put(63,50){$s_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{anypolygon2.pdf}\put(20,-3){\small{Case 2: $s_1$ contacts boundary}}\put(20,40){$s_2$}\put(55,58){$s_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{anypolygon3.pdf}\put(-6,-3){\small{Polygon generated by first contacts along $\overline{ p_i p_{i+1}}$ }}
\end{overpic}
\caption{\label{fig:polygonAlg}{ Steps to generate  the 2-move reachable set when  one particle collides with edge $\overline{ p_i p_{i+1}}$ of a convex polygonal workspace.}
\vspace{-1em}
}
\end{figure*}
 Figure \ref{fig:polygon} shows six workspaces, their $\Delta$ configuration spaces, and the 2-move reachable sets that correspond to representative initial conditions.
 Figure \ref{fig:TwoRegions} highlights the construction of the 2-move reachable sets for a square workspace. There are four 2-move reachable sets, but the horizontal (and vertical) reachable sets are equivalent in the $\Delta$ configuration space so we can plan in this space and choose between the two options to minimize the total distance.
 % The \emph{2-move reachable set} is the locus of points in the $\Delta$ configuration space corresponding to any two-move sequence where the first move brings one particle into contact with the boundary, and the second move translates the second particle without moving the first. 
Algorithm \ref{alg:polygonReachbale} computes the 2-move reachable set for any convex workspace.
The set is constructed by considering each edge of the workspace. We name each vertex as $p_i$ where $1\leq i \leq n$.
  If one particle contacts edge $\overline{ p_i p_{i+1}}$ before the other (one particle will always contact before the other unless the particles are parallel to the wall), the corresponding 2-move reachable set is a polygon, constructed in lines 2-13 of Alg.~\ref{alg:polygonReachbale}. The union of these polygons for all $n$ sides is the 2-move reachable set of $\Delta$ configurations.
Figure~\ref{fig:polygonAlg} illustrates the procedure to construct the  2-move reachable set generated by collisions with the $\overline{ p_i p_{i+1}}$ edge.
% 
 \begin{algorithm}[htb]
\caption{ { \sc ReachableSetPolygon}($s_1,s_2,g_1,g_2, P$)}\label{alg:polygonReachbale}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of starting $(s_1,s_2)$ and goal $(g_1,g_2)$ positions of  two particles. 
$P$ is a list of the vertices of a convex polygon. %RSet contains all the reachable polygons.
\State $R_{\textrm{SET}\gets \{\}}$
\For {$p_i$ in $P$}
\State $p_{i}' \gets s_1 + s_2 - p_i$
\State $p_{i+1}' \gets s_1 + s_2 - p_{i+1}$
\State $L \gets \overline{ p_i' p_{i+1}'}$ \Comment{line $(p_{i}', p_{i+1}')$}
\State $l_i, l_{i+1} \gets $ intersections of $L$ and polygon $P$
\If {$p_{i}'$ not inside polygon $P$}
\State $p_{i}' \gets l_i$
\EndIf
\If {$p_{i+1}'$ not inside polygon $P$}
\State $p_{i+1}' \gets l_{i+1}$
\EndIf
%\State $D \gets$ All vertices $\in [ l_i , l_{i+1} ] $
\State $D \gets$ $s_2 - s_1 -([l_i, v_{\textrm{min}}, ..., p_i ] -p_i' $,
